\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\begin{center}
    {\Huge \scshape Jincong Li} \\ \vspace{1pt}
    5955 Student Union Blvd, Vancouver, BC \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 778-227-0379 ~ \href{mailto:Conroycong@outlook.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{Conroycong@outlook.com}} ~ 
    \href{https://linkedin.com/in/jincong-li-33a23719a/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jincong-li-33a23719a}}  ~
    \vspace{-8pt}
\end{center}

\begin{flushright}
\today \\
\end{flushright}


Kardium \\
Burnaby, BC, Canada

Dear HR Team,

I am writing to express my interest in the Junior Mechanical Test Engineer position at Kardium, as advertised. With a Master’s degree in Mechanical Engineering from the University of British Columbia and hands-on experience in mechanical systems and experimental design, I am eager to contribute to your team and support the development of innovative medical devices like the Globe® Pulsed Field System.

During my academic and professional career, I have gained significant experience in fluid dynamics, mechanical design, and statistical analysis. My projects, such as the \textit{Model Analysis on Ship Hulls under Different Wave Conditions} and the \textit{Pressurized Experimental Device} design, have honed my skills in using advanced tools like SolidWorks, ANSYS Fluent, and MATLAB. Additionally, my internship at Lilin Group provided practical experience in metal processing and precision engineering, further enhancing my technical abilities.

Kardium’s commitment to improving lives through innovative medical technology deeply resonates with my professional values and aspirations. I am particularly impressed by the company’s collaborative environment and dedication to continuous improvement. The opportunity to work on verification and validation activities, design test jigs and fixtures, and interact with multidisciplinary teams is highly appealing to me.

Key highlights of my qualifications include:

\begin{itemize}
    \item Strong background in mechanical systems and experimental design.
    \item Proficient in using SolidWorks, ANSYS Fluent, MATLAB, and other relevant tools.
    \item Hands-on experience with mechanical/hardware product testing and data analysis using Excel and Minitab.
    \item Excellent collaboration, interpersonal, and technical documentation skills.
    \item Ability to manage multiple tasks with a high degree of accuracy and timeliness.
\end{itemize}

I am enthusiastic about the possibility of contributing to Kardium’s innovative projects and am confident that my skills and experiences align well with the requirements of this role. I have attached my resume for your review and would greatly appreciate the opportunity to discuss how I can contribute to your team. Thank you for considering my application.

Sincerely,

Jincong Li

\end{document}
