\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\begin{center}
    {\Huge \scshape Jincong Li} \\ \vspace{1pt}
    5955 Student Union Blvd, Vancouver, BC \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 778-227-0379 ~ \href{mailto:Conroycong@outlook.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{Conroycong@outlook.com}} ~ 
    \href{https://linkedin.com/in/jincong-li-33a23719a/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jincong-li-33a23719a}}  ~
    \vspace{-8pt}
\end{center}

\begin{flushright}
July 16th, 2024 \\
\end{flushright}

Seaspan \\

Dear HR Team, 

I am writing to express my interest in joining Seaspan and to inquire about potential opportunities that align with my background and skills. I am a recent graduate with a Master’s degree in Mechanical Engineering from the University of British Columbia and extensive experience in CFD and FEA simulations.

Throughout my academic and professional career, I have developed a strong foundation in fluid dynamics, mechanical design, and hands-on proficiency with tools like SolidWorks and ANSYS Fluent. My projects, such as the "Model Analysis on Ship Hulls under Different Wave Conditions," have equipped me with the technical skills required to excel in the marine transportation and shipbuilding industry. Additionally, my internship at Lilin Group provided practical experience in metal processing and precision engineering.

Seaspan’s commitment to innovation, safety, and environmental responsibility deeply resonates with my professional values and aspirations. I am particularly impressed by your efforts in marine transportation and shipbuilding, and I am enthusiastic about the prospect of contributing to such impactful work. The opportunity to work in a dynamic team environment and contribute to cutting-edge technology in the marine industry makes Seaspan my top choice for advancing my career.

I have attached my resume for your review. I would greatly appreciate the opportunity to discuss how my skills and experiences align with Seaspan’s needs and explore any potential openings within your team. Thank you for considering my application. I look forward to the possibility of contributing to Seaspan’s continued success.

Sincerely,

Jincong Li

\end{document}
