\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generated pdf is machine readable/ATS parsable
\pdfgentounicode=1

\begin{document}

\begin{center}
    {\Huge \scshape Jincong Li} \\ \vspace{1pt}
    5955 Student Union Blvd, Vancouver, BC \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 778-227-0379 ~ \href{mailto:Conroycong@outlook.com}{\raisebox{-0.2\height}\faEnvelope\ \underline{Conroycong@outlook.com}} ~ 
    \href{https://linkedin.com/in/jincong-li-33a23719a/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jincong-li-33a23719a}}  ~
    \vspace{-8pt}
\end{center}

\begin{flushright}
July 4th, 2024 \\
\end{flushright}


Dear WSP,

I am writing to express my interest in the Junior Engineer position within the advanced water modeling team at WSP, as advertised. With a Master’s degree in Mechanical Engineering from the University of British Columbia and hands-on experience in hydraulic transient modeling, I am eager to contribute to your team and further develop my skills with some of the industry's top experts.

During my academic and professional career, I have gained significant experience in hydraulic modeling and analysis. My coursework and projects, such as the \textit{Model Analysis on Ship Hulls under Different Wave Conditions} and the \textit{Pressurized Experimental Device} design, have honed my skills in using advanced tools like Ansys Fluent, Solidworks, and MATLAB. Additionally, my internship at Lilin Group provided practical experience in metal processing and precision engineering, further enhancing my technical abilities.

I am particularly excited about the opportunity at WSP due to the company's commitment to innovation, inclusion, and sustainability. I am enthusiastic about the chance to work on cutting-edge technologies and tools, such as CFD and transient analysis, and to contribute to impactful projects at local, national, and international scales. My strong analytical skills, technical proficiency, and ability to communicate complex engineering concepts clearly align well with the qualifications for this position.

Key highlights of my qualifications include:

\begin{itemize}
    \item Proven experience in hydraulic transient modeling and analysis.
    \item Proficient in using tools such as Ansys Fluent, Simflow, Abaqus, Solidworks, and MATLAB.
    \item Hands-on experience with computer-aided engineering and manufacturing tools.
    \item Strong report writing and analytical skills.
    \item Ability to collaborate effectively with multidisciplinary teams and provide critical technical input for design reviews.
\end{itemize}

I am eager to bring my expertise to WSP and contribute to advancing your hydraulic engineering projects. The opportunity to grow within a team dedicated to innovation and excellence in hydraulic modeling is particularly appealing to me.

Thank you for considering my application. I look forward to the opportunity to discuss how my skills and experiences align with the goals of WSP. Please feel free to contact me at 778-227-0379 or \href{mailto:Conroycong@outlook.com}{Conroycong@outlook.com} to schedule an interview.

Sincerely,

Jincong Li

\end{document}
