%-------------------------
% Resume in Latex
% Author : Jincong Li
%------------------------

\documentclass[letterpaper,11pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}
\usepackage{multicol}
\setlength{\multicolsep}{-3.0pt}
\setlength{\columnsep}{-1pt}
\input{glyphtounicode}


%----------FONT OPTIONS----------
% sans-serif
% \usepackage[sfdefault]{FiraSans}
% \usepackage[sfdefault]{roboto}
% \usepackage[sfdefault]{noto-sans}
% \usepackage[default]{sourcesanspro}

% serif
% \usepackage{CormorantGaramond}
% \usepackage{charter}


\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.6in}
\addtolength{\evensidemargin}{-0.5in}
\addtolength{\textwidth}{1.19in}
\addtolength{\topmargin}{-.7in}
\addtolength{\textheight}{1.4in}

\urlstyle{same}

\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% Sections formatting
\titleformat{\section}{
  \vspace{-4pt}\scshape\raggedright\large\bfseries
}{}{0em}{}[\color{black}\titlerule \vspace{-5pt}]

% Ensure that generate pdf is machine readable/ATS parsable
\pdfgentounicode=1

%-------------------------
% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-2pt}}
  }
}

\newcommand{\classesList}[4]{
    \item\small{
        {#1 #2 #3 #4 \vspace{-2pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-2pt}\item
    \begin{tabular*}{1.0\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & \textbf{\small #2} \\
      \textit{\small#3} & \textit{\small #4} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubSubheading}[2]{
    \item
    \begin{tabular*}{0.97\textwidth}{l@{\extracolsep{\fill}}r}
      \textit{\small#1} & \textit{\small #2} \\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{1.001\textwidth}{l@{\extracolsep{\fill}}r}
      \small#1 & \textbf{\small #2}\\
    \end{tabular*}\vspace{-7pt}
}

\newcommand{\resumeSubItem}[1]{\resumeItem{#1}\vspace{-4pt}}

\renewcommand\labelitemi{$\vcenter{\hbox{\tiny$\bullet$}}$}
\renewcommand\labelitemii{$\vcenter{\hbox{\tiny$\bullet$}}$}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0.0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{-5pt}}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%


\begin{document}

%----------HEADING----------
% \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
%   \textbf{\href{http://sourabhbajaj.com/}{\Large Sourabh Bajaj}} & Email : \href{mailto:sourabh@sourabhbajaj.com}{sourabh@sourabhbajaj.com}\\
%   \href{http://sourabhbajaj.com/}{http://www.sourabhbajaj.com} & Mobile : +1-123-456-7890 \\
% \end{tabular*}

\begin{center}
    {\Huge \scshape Jincong Li} \\ \vspace{1pt}
    5955 Student Union Blvd, Vancouver, BC \\ \vspace{1pt}
    \small \raisebox{-0.1\height}\faPhone\ 778-227-0379 ~ \href{mailto:x@gmail.com}{\raisebox{-0.2\height}\faEnvelope\  \underline{Conroycong@outlook.com}} ~ 
    \href{https://linkedin.com/in/jincong-li-33a23719a/}{\raisebox{-0.2\height}\faLinkedin\ \underline{linkedin.com/in/jincong-li-33a23719a}}  ~
    \vspace{-8pt}
\end{center}


%-----------EDUCATION-----------
\section{Education}
  \resumeSubHeadingListStart
    \resumeSubheading
      {The University of British Columbia}{Sep. 2023 -- Sep. 2024}
      {Master of Mechanical Engineering}{Vancouver, BC}
    \resumeSubheading
      {The University of British Columbia}{Sep. 2018 -- May. 2023}
      {Bachelor of Applied Science}{Vancouver, BC}
  \resumeSubHeadingListEnd

%------RELEVANT COURSEWORK-------
\section{Relevant Coursework}
    %\resumeSubHeadingListStart
        \begin{multicols}{4}
            \begin{itemize}[itemsep=-5pt, parsep=3pt]
                \item Fluid-Structure Interaction
                \item Finite Element Method/Analysis
                \item Computational Fluid Dynamics
                %\item Thermodynamics
                \item Fluid Mechanics
                \item Aircraft Aerodynamic
                \item Aerospace Propulsion System
                % \item Automatic Control
                \item Mechanical Vibration Analysis
                \item Mechanics of Materials
                \item Calculus of Variation
                \item Engineering Data Analysis
            \end{itemize}
        \end{multicols}
        \vspace*{2.0\multicolsep}
    %\resumeSubHeadingListEnd


%-----------EXPERIENCE-----------
\section{Experience}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Lilin Group }{May 2020 -- August 2020}
      {Metal Treatment Engineer Internship}{Tianjin, China}
      \resumeItemListStart
        \resumeItem{Acquired expertise in transporting raw materials utilizing hoisting equipment.}
        \resumeItem{Gained hands-on experience in the intricacies of metal processing, encompassing processes such as tempering, smithing, and casting, contributing to a nuanced understanding of metallurgical techniques.}
        \resumeItem{Operated CNC lathe and milling machines, showcasing adeptness in utilizing cutting-edge machinery for precision engineering tasks.}
        \resumeItem{Studied the distinctive performance attributes of steel with varying compositions and corresponding percentage content, developing a nuanced comprehension of metallurgical properties.}
      \resumeItemListEnd
  \resumeSubHeadingListEnd
\vspace{-15pt}

%-----------PROJECTS-----------
\section{Projects}
    \vspace{-10pt}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Model Analysis on Ship Hulls under Different Wave Conditions} $|$ \emph{Simflow, Gmsh, Abaqus, Calculix}}{May 2024}
          \resumeItemListStart
            \resumeItem{Worked on Solidworks and  Gmsh to create the required domain then mesh it with tests of convergence.}
            \resumeItem{Run simulations with mesh motion (ALE) and multi-phase flow using simflow on Sockeye from UBC as well as on Beluga from computecanada.}
            \resumeItem{Conducted frequency/vibration analysis on ship hulls, such as DTMB 5415 and BURNSi (Benchmark Underwater Radiated
            Noise Simulations) models.}
            \resumeItem{Modified the solver files written in C to simulate the waves/sea states.}
          \resumeItemListEnd 
          \vspace{-20pt}
        \resumeProjectHeading
          {\textbf{Pressurized Experimental Device} $|$ \emph{CFD(Ansys Fluent), Solidworks, Abaqus}}{September 2022}
          \resumeItemListStart
            \resumeItem{Designed and built a device for a complex fluid laboratory to study the behavior of air bubbles travelling in non- newtonian fluid.}
            \resumeItem{Designed and modelled the supporting base in Solidworks and validated its performance in Abaqus. Then built it out of 8020s, during which gained practical experience in constructing 8020s.}
           % Related aerodynamics analysis was done by Ansys and XLFR5
            \resumeItem{Learned technical knowledge of sealing structure in pressurized device and relevant regulations such as CSA B51.}
            \resumeItem{Developed project management skills especially in budget estimating and controlling. Gained experience in handling unexpected situations during the project such as requirement change and communication barrage.}
          \resumeItemListEnd
          \vspace{-20pt}
      \resumeProjectHeading
          {\textbf{Wing Design for Cargo Plane} $|$ \emph{CFD(Ansys Fluent), XFLR5, MATLAB}}{November 2021}
          \resumeItemListStart
            \resumeItem{Designed a flapped wing for a cargo plane for the highest takeoff weight, least flight time and least fuel consumption under given constraints.}
            \resumeItem{Modelled the plane in MATLAB mathematically to track its performance in the taking-off, cruising and landing conditions.}
           % Related aerodynamics analysis was done by Ansys and XLFR5
            \resumeItem{Optimized the lift and drag coefficient of the wing by modelling it in Ansys and XFLR5 and tuning the shape of the airfoil and flap of the wing .}
          \resumeItemListEnd
          \vspace{-20pt}
%         \resumeProjectHeading
%          {\textbf{Permeability of Medical Face Mask} $|$ \emph{MATLAB, Arduino}}%{February 2021}
%          \resumeItemListStart
%            \resumeItem{Revealed the behavior of melt-blown fabric’s %permeability under the humidity condition of human breath.}
%            \resumeItem{Developed the permeability-time correlation by measuring the differential pressure across the melt-blown fabric and using a humidifier to simulate human breath moisture.}
%            \resumeItem{Build and encode a humidity and pressure senor on Arduino. Integrated the Arduino with MATLAB to acquire data.}
%          \resumeItemListEnd 
%          \vspace{-20pt}
      \resumeProjectHeading
          {\textbf{Powered Air Purifying Respirator for Bus Drivers} $|$ \emph{Solidworks, MATLAB}}{October 2020}
          \resumeItemListStart
            \resumeItem{Designed and modelled a device consisting of a headpiece that fits over the driver’s head, a pipe that connects the headpiece, through a threaded attachment, to the filter system, and a blow-box that contains a pump that drives the airflow through the PAPR and the filter to remove COVID-19 particle.}
            \resumeItem{Estimated the average cost of the PAPR according to the real price of each component and compare with other existing commercial PAPRs.}
          \resumeItemListEnd 
          \resumeSubHeadingListEnd
           \vspace{25pt}
%     \resumeProjectHeading
%          {\textbf{Rover} \emph}{March 2019}
%          \resumeItemListStart
%            \resumeItem{Designed a Rover with sustainable and light materials that can move in different road condition.}
%            \resumeItem{Experienced the entire design process including project management, functional decomposition, conceptual solution and concept evaluation.}
%          \resumeItemListEnd 
%          \resumeSubHeadingListEnd
%   \vspace{-3pt}
%
%-----------PROGRAMMING SKILLS-----------

\section{Technical Skills}
 \begin{itemize}[leftmargin=0.15in, label={}]
    \small{\item{
     \textbf{Languages}{: MATLAB, Python}\\
     \textbf{Modelling \& Analysis Tools}{: Simflow, Abaqus, Solidworks, Ansys Fluent, XFLR5(aerodynamic), MATLAB\&Simulink, Arduino} \\
     \textbf{Basic Tools}{: Office, Latex} \\
    }}
 \end{itemize}
 \vspace{-16pt}



\end{document}
